### 2016-02-25 config/glossaries.inc.tex
Table with different stress test cases
Some work on init-vals
Corrections Johan: ch05 (part 1) + compu complex
Some changes from Tom
Improve CH02
Fix glspl on first use

\renewcommand{\newacronym}[4][]{\newglossaryentry{#2}{type=\acronymtype,
name={#3},
description={#4},
text={#3},
first={#4~(#3)},
plural={#3\glspluralsuffix},
firstplural={#4~(#3\glspluralsuffix)},
#1}}

@@

\newsymbolglos{A-SetC}{\ComplexNumbers}{Set of the complex numbers}
\newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
\newsymbolglos{A-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
\newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
\newsymbolglos{A-SetRneg}{\NegativeRealNumbers}{Set of negative real numbers}
\newsymbolglos{A-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
\newsymbolglos{A-SetQ}{\RationalNumbers}{Set of the rational numbers}
\newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
\newsymbolglos{A-SetZ}{\IntegerNumbers}{Set of integer numbers}

@@

\newsymbolglos{E-approx}{\approx}{is approximately equal to \ldots}
\newsymbolglos{E-bydef}{\isdef}{is defined as \ldots}
\newsymbolglos{E-propto}{\propto}{is proportional to \ldots}
\newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}

@@

\newacronym{BLA}{BLA}{\abbrev{b}est \abbrev{l}inear \abbrev{a}pproximation}
\newacronym{BK}{B\&K}{\bruelkjaer}
\newacronym{BTLS}{BTLS}{\abbrev{b}ootstrapped \abbrev{t}otal \abbrev{l}east \abbrev{s}quares}

\newacronym{CRLB}{CRLB}{Cramér-Rao lower bound}
\newacronym{CZT}{CZT}{chirp $Z$-transform}

\newacronym{DC}{DC}{direct current (also: mean value)}
\newacronym{DCkernel}{DC kernel}{diagonal correlated kernel}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{FFT}{FFT}{fast Fourier transform}
\newacronym{FRF}{FRF}{frequency response function}

@@

@@

\newacronym{PSD}{PSD}{power spectral density}

\newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
\newacronym{RFIR}{RFIR}{\abbrev{r}egularized \abbrev{f}inite \abbrev{i}mpulse \abbrev{r}esponse}
\newacronym{RMS}{RMS}{\abbrev{r}oot-\abbrev{m}ean-\abbrev{s}quare}
\newacronym{RMSE}{RMSE}{\abbrev{r}oot \abbrev{m}ean \abbrev{s}quared \abbrev{e}rror}

@@

\newacronym{TRIMM}{TRIMM}{Transient Impulse Modeling}

>>>>

\renewcommand{\newacronym}[4][]{\newglossaryentry{#2}{type=\acronymtype,
name={#3},
description={#4},
text={#3},
first={#4~(#3)},
plural={#3\glspluralsuffix},
firstplural={#4\glspluralsuffix~(#3\glspluralsuffix)},
#1}}

@@

\newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
\newsymbolglos{A-SetZ}{\IntegerNumbers}{Set of integer numbers}
\newsymbolglos{A-SetQ}{\RationalNumbers}{Set of the rational numbers}
\newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
\newsymbolglos{A-SetC}{\ComplexNumbers}{Set of the complex numbers}
\newsymbolglos{A-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
\newsymbolglos{A-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
\newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
\newsymbolglos{A-SetRneg}{\NegativeRealNumbers}{Set of negative real numbers}

@@

\newsymbolglos{E-approx}{\approx}{is approximately equal to \ldots}
\newsymbolglos{E-bydef}{\isdef}{is defined as \ldots}
\newsymbolglos{E-propto}{\propto}{is proportional to \ldots}
\newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}
\newsymbolglos{E-ll}{\ll}{is much smaller than \ldots}
\newsymbolglos{E-gg}{\gg}{is much greater than \ldots}

@@

\newacronym{ADC}{ADC}{analog-to-digital converter}

\newacronym{BLA}{BLA}{\abbrev{b}est \abbrev{l}inear \abbrev{a}pproximation}
\newacronym{BK}{B\&K}{\bruelkjaer}
\newacronym{BNC}{BNC}{Bayonet Neill-Concelman (connector)}
\newacronym{BTLS}{BTLS}{\abbrev{b}ootstrapped \abbrev{t}otal \abbrev{l}east \abbrev{s}quares}

\newacronym{CDF}{CDF}{cumulative distribution function}
\newacronym{CPU}{CPU}{central processing unit}
\newacronym{CRLB}{CRLB}{Cramér-Rao lower bound}
\newacronym{CZT}{CZT}{chirp $Z$-transform}

\newacronym{DAC}{DAC}{digital-to-analog converter}
\newacronym{DC}{DC}{direct current (also: mean value)}
\newacronym{DCkernel}{DC kernel}{diagonal correlated kernel}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{FFT}{FFT}{fast Fourier transform}
\newacronym{FIR}{FIR}{finite impulse response}
\newacronym{FRF}{FRF}{frequency response function}

@@

\newacronym{NI}{NI}{National Instruments}

@@

\newacronym{PDF}{PDF}{probability distribution function}
\newacronym{PSD}{PSD}{power spectral density}

\newacronym{RAM}{RAM}{random-access memory}
\newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
\newacronym{RFIR}{RFIR}{\abbrev{r}egularized \abbrev{f}inite \abbrev{i}mpulse \abbrev{r}esponse}
\newacronym{RMS}{RMS}{\abbrev{r}oot-\abbrev{m}ean-\abbrev{s}quare}
\newacronym{RMSE}{RMSE}{\abbrev{r}oot \abbrev{m}ean \abbrev{s}quared \abbrev{e}rror}

@@

\newacronym{TF}{TF}{transfer function}
\newacronym{TRIMM}{TRIMM}{Transient Impulse Modeling}
